Comparison of Terrain Following and Cut Cell Grids using a Non-Hydrostatic Model

### 2015-05-18 fig-advection-tracer.tex
Merge tracer and error contours into single figure
Added 4th order plots from schaer's code, just need to rearrange
everything to fit on a 3x2 grid of panels.
Plot six panels for advection tracer/error contour

\documentclass{article}
\usepackage[paperwidth=3in,paperheight=4.6in,margin=0in]{geometry}
\usepackage{mathptmx}%{times}
\usepackage{graphicx}
\usepackage{siunitx}

\setlength{\parindent}{0pt}
\begin{document}
\hspace{0.15in}\includegraphics[width=2.75in]{img/schaer-btf-4thorder.png}

\footnotesize
\input{../advectTracer-horizontal-btf-cubicUpwindCPCFit-divFree/tracer-contour-y-only}

\input{../advectTracer-horizontal-snapCol-cubicUpwindCPCFit-divFree/tracer-contour}
\end{document}

>>>>

\documentclass{article}
\usepackage[paperwidth=6.4in,paperheight=4.6in,margin=0in]{geometry}
\usepackage{mathptmx}%{times}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[absolute,overlay]{textpos}

\setlength{\parindent}{0pt}
\begin{document}
\input{../advection-horizontal-contours/contours}
\end{document}
